### 2014-03-27 LaTeX/RhodiumLit.tex
Added a little theory.  Just syncing for the hell of it

>>>>

\cite{imai:weinstein:2000} explored the differing economic impacts of civil war by distinguinshing between those conflicts cover larger or smaller geographic areas.  Using a variety of regression techniques, they find that there is a negative correlation between geographical spread of conflict and the decade average of economic growth for each country.  Widespread conflicts, they argue, are more likely to result in damage to infrastructure, divestment from normal state spending, and capital flight.  However, in subsequent simulations that account for estimation and fundamental uncertainty, the authors show that these results are uncertain and should be interpreted with caution.

### 2014-03-27 LaTeX/RhodiumTheory.tex
Added a little theory.  Just syncing for the hell of it

Finally, the perception of violence near major cities and resource centers should negatively impact foreign investment.  Investors will react negatively to news that violence is occuring near major cities and resources.  Investment is generally contingent on the expectation of a stable labor base and, sometimes, reliable access to resources.  Conflicts that appear to threaten these, whether they do or not, should correspond to a decrease in foreign investment.

>>>>

Finally, the perception of violence near major cities and resource centers should negatively impact foreign investment.  Investors will react negatively to news that violence is occuring near major cities and resources.  Investment is generally contingent on the expectation of a stable labor base and, sometimes, reliable access to resources.  Conflicts that appear to threaten these, whether they do or not, should correspond to a decrease in foreign investment.\footnote{While we intend to test each of these hypotheses carefully, our project in its current form addresses only the second hypothesis - the effect of conflict distance from city centers on aggregate state economic performance.  Future iterations of this paper will also include tests of the remaining hypotheses using foreign investment, economic growth, and domestic investment as dependent variables.}

While these hypotheses may resemble those of \cite{imai:weinstein:2000}, ours differs somewhat in the hypothesized mechanism through which conflict affects economic performance.  While we do not disagree that the spread of a conflict could impact state economic prospects, we argue that conflict area is not necessary for adverse economic performance.  Conflict area is only one possible proxy for overall destructiveness.  However, conflicts with smaller spatial areas can be similarly disruptive if they are centered near (and impede access to) those resources outlined above.  In fact, we feel measures of proximity rather than spread are more appropriate to test the hypothesis that conflict obstucts vital economic activity.
